Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

In total the benchmarking matrix consisted of 156 experiments (6 feature sets * 3 ML algorithms * 8 feature-selection methods + 2 * 6 L1 and L2 models).

>>>>

In total the benchmarking matrix consisted of 156 experiments (6 feature sets $\times$ 3 ML algorithms $\times$ 8 feature-selection methods + 2 $\times$ 6 L1 and L2 models).
